---
title: 
output: html_document
---
 
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(kableExtra)
library(DT)
library(downloadthis)
library(ggplot2)
```

The Single Cell Multiome ATAC + Gene Expression software suite consists of Cell Ranger ARC for the analysis of chromatin accessibility and 3' gene expression data from the same cell produced by the 10x platform.

Cell Ranger ARC performs sample demultiplexing, barcode processing, identification of open chromatin regions, and simultaneous counting of transcripts and peak accessibility in single cells. 

Additionally, the pipelines perform secondary analyses like dimensionality reduction, clustering, differential analysis, and feature linkage between peaks and genes that aid in data interpretation.

```{r, echo = FALSE}
appliation='Cell Ranger ARC v2.0';

DiagrammeR::grViz("
  digraph graph2 {
  
  graph [layout = dot, rankdir = LR]
  
  # node definitions with substituted label text
  node [shape = box, style=rounded, color=brown, fillcolor=azure3, fontsize=25]
  a [label = '@@1']
  b [label = '@@2']
  c [label = '@@3']
  d [label = '@@4']
  
  a -> b -> c -> d
  }
  
  [1]: 'bcl2fastq'
  [2]: appliation[1]
  [3]: 'Generation of metadata'
  [4]: 'Secondary analyses'
  ",
  height = 100)
```


